\documentclass[sans]{moderncv}

\usepackage[margin=2cm]{geometry}

\moderncvstyle{classic} % casual (default), classic, banking, oldstyle, fancy
\moderncvcolor{blue}    % black, blue (default), burgandy, green, grey, orange, purple, red
\moderncvicons{awesome} % awesome, marvosym

% Sets non-italic font for title and contact info
\renewcommand{\addressfont}{\normalsize\mdseries\upshape}
\renewcommand{\titlefont}{\LARGE\mdseries\upshape}

% Fixes weird off-center bullets
\renewcommand{\labelitemi}{\color{color1}\raisebox{0.5pt}{$\circ$}}

% =============================================================================

\name{Matt}{Dutson}
\title{CS Graduate Student at UW-Madison}
\phone{(608) 440-4434}
\email{dutson@wisc.edu}
\homepage{mattdutson.net}

% =============================================================================

\begin{document}

\makecvtitle

% =============================================================================

\section{Education}

\cventry{2018--Present}{MS/PhD in Computer Science}{University of Wisconsin-Madison}{Madison WI}{}{
    Interests: Computer vision, computer graphics, machine learning
}

\cventry{2013--2018}{Honors BS in Physics}{University of Utah}{Salt Lake City UT}{\textit{magnum cum laude}}{
    Minors: Computer science, mathematics \newline
    Thesis: Reconstruction of Cosmic Ray Geometry Using Cherenkov Backscattering
}

% =============================================================================

\section{Publications}

\cvitem{2020}{
    \textbf{Fibrillar Collagen Quantification With Curvelet Transform Based Computational Methods} \newline
    \textit{Frontiers in Bioengineering and Biotechnology} \newline
    Y.\ Liu, A.\ Keikhosravi, C.\ Pehlke, J.\ Bredfeldt, \textbf{M.\ Dutson}, H.\ Liu, G.\ Mehta, R.\ Claus, A.\ Patel, M.\ Conklin, D.\ Inman, P.\ Provenzano, E.\ Sifakis, J.\ Patel, and K.\ Eliceiri
}

% =============================================================================

\section{Technical Skills}

\cvitem{Languages}{\textbf{C++}, \textbf{Java}, \textbf{Python}, \textbf{Rust}, C, C\#, JavaScript, Perl}

\cvitem{Machine Learning}{\textbf{TensorFlow}, PyTorch, scikit-learn}

\cvitem{Scientific}{\textbf{NumPy}, MATLAB}

\cvitem{High Performance}{CUDA, MPI, OpenMP}

\cvitem{Other}{\textbf{Linux}, \textbf{UNIX}, Git, LaTeX}

% =============================================================================

\section{Selected Coursework}

\cvitem{Computer Science}{Computer vision, computer graphics, machine learning, high performance computing, nonlinear optimization, algorithms, machine organization}

\cvitem{Mathematics}{Real analysis, statistics, partial differential equations, ordinary differential equations, linear algebra, calculus}

\cvitem{Physics}{Particle physics, quantum mechanics, special relativity, thermodynamics, classical physics}

% =============================================================================

\section{Industry Experience}

\cventry{2019}{Map Exploration Software Intern}{Esri}{Redlands CA}{}{
    \begin{itemize}
        \item Designed and implemented algorithms for high-performance viewshed analysis.
        \item Built an integrated machine learning application for automatically detecting building features in 3D urban scenes.
    \end{itemize}
}

\cventry{2017}{Process Software Intern}{IM Flash Technologies}{Lehi UT}{}{
    \begin{itemize}
        \item Improved the efficiency of wafer defect sourcing using an automated Perl pipeline.
        \item Reduced errors in process time estimation by 97 percent via online statistical analysis of historical data.
    \end{itemize}
}

\cventry{2016}{Process Software Intern}{IM Flash Technologies}{Lehi UT}{}{
    \begin{itemize}
        \item Created a C++ OpenCV computer vision application which successfully detected manufacturing equipment failures.
    \end{itemize}
}

% =============================================================================

\section{Research Experience}

\cventry{2020--Present}{Research Assistant}{UW-Madison}{}{Advised by Mohit Gupta}{
    \begin{itemize}
        \item Creating image and video processing algorithms for single-photon visual sensors.
        \item Exploring theory and applications of spiking neural networks.
    \end{itemize}
}

\cventry{2018--2019}{Research Assistant}{UW-Madison}{}{Advised by Jignesh Patel and Kevin Eliceiri}{
    \begin{itemize}
        \item Participated in the initial design and development of Hustle, a scalable replacement for SQLite written in Rust.
        \item Built a Java application for generating synthetic images of biological fiber networks.
    \end{itemize}
}

\cventry{2016--2018}{Research Assistant}{University of Utah}{}{Advised by Douglas Bergman}{
    \begin{itemize}
        \item Wrote C++ simulations of cosmic ray propagation and detection in order to test new detection techniques.
        \item Operated the Telescope Array observatory in Delta UT.
    \end{itemize}
}

% =============================================================================

\section{Teaching Experience}

\cventry{Fall 2019}{Teaching Assistant}{UW-Madison}{}{CS 559 Computer Graphics}{
    Instructor: Florian Heimerl
}

\cventry{Fall 2017}{Teaching Assistant}{University of Utah}{}{CS 2100 Discrete Structures}{
    Instructor: Bei Wang
}

\cventry{Spring 2017}{Teaching Assistant}{University of Utah}{}{PHYS 2020 General Physics II}{
    Instructor: Ren Pankovich
}

\cventry{Fall 2016}{Teaching Assistant}{University of Utah}{}{PHYS 2010 General Physics I}{
    Instructor: Orest Symko
}

\cventry{2015--2016}{Private Physics Tutor}{University of Utah}{}{}{
    Courses: General Physics I and II, Physics for Scientists and Engineers I and II, Introduction to Quantum Theory and Relativity
}

% =============================================================================

\section{Volunteer Experience}

\cventry{2019--Present}{Events Committee Chair}{Student ACM Chapter}{Madison WI}{}{
    \begin{itemize}
        \item Responsible for overseeing department-wide, student-organized events.
        \item Coordinated with the CS department in planning and hosting the 2020 prospective graduate student welcome weekend event.
    \end{itemize}
}

\cventry{2019}{Events Committee Officer}{Student ACM Chapter}{Madison WI}{}{}

\cventry{2018}{CS Club Leader}{Lowell Elementary School}{Madison WI}{}{
    \begin{itemize}
        \item Coached 4\textsuperscript{th} and 5\textsuperscript{th} graders in Scratch programming and computational thinking.
    \end{itemize}
}

\cventry{2016, 2017}{Project Judge}{Salt Lake Valley Science and Engineering Fair}{Salt Lake City UT}{}{}

% =============================================================================

\end{document}
