\documentclass[12pt]{article}

\usepackage[letterpaper, margin=0.5in]{geometry}

\usepackage{titlesec}
\titleformat{\section}
    {\large \bfseries}{\thesection}{}{}[{\titlerule[0.5pt]}]
\titlespacing{\section}
    {0pt}{0.7em}{0.5em}

\usepackage{palatino}
\newcommand{\setfont}{\fontfamily{ppl} \selectfont}

\usepackage{enumitem}
\renewcommand{\labelitemi}{--}
\setlist[itemize]{noitemsep, topsep=0.2em, leftmargin=0.3in}

\newcommand{\blockskip}{\vspace{0.7em}}

\newcommand{\tabsize}{\hspace{5.2in}}

\newenvironment{tab1}
    {\bfseries \begin{tabbing} \tabsize \= \kill}{\end{tabbing}}

\newenvironment{tab2}
    {\begin{tabbing} \tabsize \= \kill}{\end{tabbing}}

\setlength{\parindent}{0em}
\setlength{\topsep}{0.1em}
\setlength{\partopsep}{0em}


\begin{document}

\setfont
\pagestyle{empty}


\begin{center}
    {\LARGE \bfseries Matthew Dutson}\\
    \medskip
    mdutson.net\\
    (435) 720-1369 \enspace dutson@wisc.edu
\end{center}


\section*{Education}

\begin{tab1} University of Wisconsin-Madison \> Madison, Wisconsin \end{tab1}
\begin{tab2} MS/PhD in Computer Science \> Fall 2018 - Present \end{tab2}

\begin{itemize}
    \item Interests: Computer vision, graphics, machine learning
\end{itemize}

\blockskip

\begin{tab1} University of Utah \> Salt Lake City, Utah \end{tab1}
\begin{tab2} Honors Bachelor of Science in Physics \> Fall 2013 - Spring 2018 \end{tab2}

\begin{itemize}
    \item Magnum cum laude
    \item Minors: Computer science, mathematics
    \item Thesis: Reconstruction of Cosmic Ray Geometry Using Cherenkov Backscattering
\end{itemize}


\section*{Coursework and Languages}

\begin{tabular}{ @{} p{1.75in} p{5.5in} }
Selected coursework & Machine learning, artificial intelligence, computer graphics, algorithms, scientific computing, linear algebra, statistics, differential equations \\
Most experience & C++, Python, Java, Rust \\
Some experience & C, C\#, Perl, JavaScript, LaTeX, Linux/UNIX
\end{tabular}


\section*{Work Experience}

\begin{tab1} Esri \> Redlands, California \end{tab1}
\begin{tab2} Map Exploration Software Intern \> Summer 2019 \end{tab2}
\begin{itemize}
    \item Creating tools for high-performance visibility analysis in ArcGIS Pro.
    \item Leveraging machine learning for detecting objects in 3D urban scenes.
\end{itemize}

\blockskip

\begin{tab1} UW-Madison Computer Sciences \> Madison, Wisconsin \end{tab1}
\begin{tab2} Graduate Research Assistant \> Fall 2018 - Spring 2019 \end{tab2}
\begin{itemize}
    \item Collaborator on Hustle, a scalable replacement for SQLite written in Rust.
    \item Wrote a Java application to generate synthetic images of biological fiber networks.
\end{itemize}

\blockskip

\begin{tab1} University of Utah Physics \& Astronomy \> Salt Lake City, Utah \end{tab1}
\begin{tab2} Undergraduate Research Assistant \> Spring 2016 - Summer 2018 \end{tab2}
\begin{itemize}
    \item Conducted research on atmospheric cosmic ray detection techniques.
    \item Operated the Telescope Array observatory in Delta, Utah.
\end{itemize}

\blockskip

\begin{tab1} University of Utah School of Computing \> Salt Lake City, Utah \end{tab1}
\begin{tab2} Teaching Assistant \> Fall 2017 \end{tab2}
\begin{itemize}
    \item Course: CS 2100 - Discrete Mathematics
    \item Responsible for leading weekly discussions and creating homework solutions.
\end{itemize}

\blockskip

\begin{tab1} IM Flash Technologies \> Lehi, Utah \end{tab1}
\begin{tab2} Process Software Intern \> Summer 2017, Summer 2018 \end{tab2}
\begin{itemize}
    \item Wrote Perl scripts to improve the efficiency of manufacturing defect sourcing.
    \item Improved existing software to reduce errors in process time estimation by 97 percent.
    \item Built a C++ computer vision application for detecting equipment malfunctions.
\end{itemize}

\end{document}