\input{resume_preamble}

\usepackage{bibentry}

\begin{document}

\nobibliography{publications}
\bibliographystyle{acm}

\setfont
\pagestyle{empty}

\begin{center}
    {\LARGE \bfseries Matthew Dutson} \\
    \medskip
    mdutson.net \\
    (608) 440-4434 \enspace dutson@wisc.edu
\end{center}

\section*{Education}

\begin{tab1} University of Wisconsin-Madison \> Madison, Wisconsin \end{tab1}

\begin{tab2} MS/PhD in Computer Science \> Fall 2018 - Present \end{tab2}
\begin{itemize}
    \item Interests: Computer vision, graphics, machine learning
\end{itemize}

\blockskip

\begin{tab1} University of Utah \> Salt Lake City, Utah \end{tab1}

\begin{tab2} Honors Bachelor of Science in Physics \> Fall 2013 - Spring 2018 \end{tab2}
\begin{itemize}
    \item Magnum cum laude
    \item Minors: Computer science, mathematics
    \item Thesis: Reconstruction of Cosmic Ray Geometry Using Cherenkov Backscattering
\end{itemize}

\section*{Publications}

\bibentry{fibrillir_collagen_quantification}

\section*{Coursework and Technologies}

\begin{tabular}{ @{} p{1.75in} p{5in} }
Selected coursework & Machine learning, computer vision, computer graphics, nonlinear optimization, algorithms, scientific computing, high performance computing, linear algebra, statistics, differential equations \\
Most experience & Python, C++, Java, Rust, UNIX, Git, NumPy, TensorFlow \\
Some experience & C, C\#, Perl, JavaScript, MATLAB, CUDA, OpenMP, MPI, PyTorch
\end{tabular}

\section*{Work Experience}

\begin{tab1} UW-Madison Computer Sciences \> Madison, Wisconsin \end{tab1}

\begin{tab2} Graduate Research Assistant \> Spring 2020 - Present \end{tab2}
\begin{itemize}
    \item Advisor: Mohit Gupta
    \item Developing techniques for interpreting data from single-photon visual sensors.
    \item Exploring theory and applications of spiking neural networks.
\end{itemize}

\begin{tab2} Graduate Research Assistant \> Fall 2018 - Spring 2019 \end{tab2}
\begin{itemize}
    \item Advisors: Jignesh Patel, Kevin Eliceiri
    \item Collaborator on Hustle, a scalable replacement for SQLite written in Rust.
    \item Wrote a Java application to generate synthetic images of biological fiber networks.
\end{itemize}

\blockskip

\begin{tab1} Esri \> Redlands, California \end{tab1}

\begin{tab2} Map Exploration Software Intern \> Summer 2019 \end{tab2}
\begin{itemize}
    \item Created tools for high-performance visibility analysis in ArcGIS Pro.
    \item Leveraged machine learning for detecting objects in 3D urban scenes.
\end{itemize}

\blockskip

\begin{tab1} University of Utah Physics \& Astronomy \> Salt Lake City, Utah \end{tab1}

\begin{tab2} Undergraduate Research Assistant \> Spring 2016 - Summer 2018 \end{tab2}
\begin{itemize}
    \item Advisor: Douglas Bergman
    \item Conducted research on atmospheric cosmic ray detection techniques.
    \item Operated the Telescope Array observatory in Delta, Utah.
\end{itemize}

\blockskip

\begin{tab1} IM Flash Technologies \> Lehi, Utah \end{tab1}

\begin{tab2} Process Software Intern \> Summer 2017 \end{tab2}
\begin{itemize}
    \item Wrote Perl scripts to improve the efficiency of manufacturing defect sourcing.
    \item Improved existing software to reduce errors in process time estimation by 97 percent.
\end{itemize}

\begin{tab2} Process Software Intern \> Summer 2016 \end{tab2}
\begin{itemize}
    \item Built a C++ computer vision application for detecting equipment malfunctions.
\end{itemize}

\section*{Teaching Assistantships}

\begin{tab1} UW-Madison Computer Sciences \> Madison, Wisconsin \end{tab1}

\begin{tab2} CS 559 - Computer Graphics \> Fall 2019 \end{tab2}

\blockskip

\begin{tab1} University of Utah School of Computing \> Salt Lake City, Utah \end{tab1}

\begin{tab2} CS 2100 - Discrete Mathematics \> Fall 2017 \end{tab2}

\blockskip

\begin{tab1} University of Utah Physics \& Astronomy \> Salt Lake City, Utah \end{tab1}

\begin{tab2} Physics 2020 - General Physics II \> Spring 2017 \end{tab2}

\begin{tab2} Physics 2010 - General Physics I \> Fall 2016 \end{tab2}

\section*{Other Experience}

\begin{tab1} UW-Madison Student ACM Chapter (SACM) \> Madison, Wisconsin \end{tab1}

\begin{tab2} Events Committee Chair \> Fall 2019 - Present \end{tab2}
\begin{itemize}
    \item Coordinated volunteer efforts for department-wide, student-led events.
    \item Worked with the CS department to plan the annual Prospective Student Welcome Weekend.
\end{itemize}

\begin{tab2} Events Committee Officer \> Spring 2019 \end{tab2}

\blockskip

\begin{tab1} Lowell Elementary School \> Madison, Wisconsin \end{tab1}

\begin{tab2} CS Club Leader \> Fall 2018 \end{tab2}
\begin{itemize}
    \item Coached 4\textsuperscript{th} and 5\textsuperscript{th} graders in Scratch programming and computational thinking.
    \item Managed behavior and attention of a large group.
\end{itemize}

\blockskip

\begin{tab1} Salt Lake Valley Science and Engineering Fair \> Salt Lake City, Utah \end{tab1}

\begin{tab2} Elementary Division Judge \> Spring 2016, Spring 2017 \end{tab2}
\begin{itemize}
    \item Evaluated projects at a regional science fair for K-12 students.
    \item Provided advice and mentorship throughout the evaluation process.
\end{itemize}

\blockskip

\begin{tab1} University of Utah College of Science \> Salt Lake City, Utah \end{tab1}

\begin{tab2} Science Day Volunteer \> Fall 2015, Fall 2016 \end{tab2}
\begin{itemize}
    \item Offered logistical support at an annual outreach event for high school students.
\end{itemize}

\begin{tab2} Private Tutor \> Summer 2015 - Spring 2016 \end{tab2}
\begin{itemize}
    \item Courses: College Algebra I, General Physics I \& II, Physics for Scientists I \& II, Introduction to Quantum Mechanics and Relativity
    \item Tutored 2-3 students each semester.
\end{itemize}

\end{document}